### 2012-02-03 GUIErrorDetector/paper/evaluation.tex
revise the algorithm and UI-accessing methods

The first variant uses DFS for graph traverse by changing
line 7 in Figure~\ref{fig:androiderror} to:
$\mathit{fringe}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
and changing queue operations (\CodeIn{enqueueAll}, \CodeIn{dequeue}, and \CodeIn{enqueue} on lines 9,
11, and 23 in Figure~\ref{fig:androiderror}, respectively)
to the corresponding statck operations (\CodeIn{pushAll}, \CodeIn{pop} and \CodeIn{push}).

>>>>

The first variant uses DFS for graph traverse by changing
line 7 in Figure~\ref{fig:androiderror} to:
$\mathit{worklist}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
and changing queue operations (\CodeIn{enqueueAll}, \CodeIn{dequeue}, and \CodeIn{enqueue} on lines 9,
11, and 23 in Figure~\ref{fig:androiderror}, respectively)
to the corresponding statck operations (\CodeIn{pushAll}, \CodeIn{pop} and \CodeIn{push}).
